### 2023-07-13 paper/sec-protonPDFs.tex
Update sec-protonPDFs.tex

%
The baseline dataset is defined as follows.
%
We consider the FASER$\nu$2 experiment integrated over the full duration of the HL-LHC data-taking period,
we account both for inclusive and charm production structure functions, we consider the scenario
in which systematic errors can be neglected, and we allow for charge separation of the outgoing lepton.
%
This baseline result therefore represents the best-case scenario and quantifies the maximum impact that can be expected
on the PDFs: we then assess to which extent variations of these input choices degrade the reach of the pseudo-data.

Fig.~\ref{fig:profiling_baseline} displays the fractional uncertainties at the 68\% confidence level
for the up and down valence quarks, total quark singlet, strangeness, charm, and gluon PDFs
in PDF4LHC21 compared to the results of its profiling with this baseline LHC neutrino dataset, namely
FASER$\nu$2 with only statistical errors, both inclusive and charm structure functions,  and charge flavour
separation.
%
The same style of PDF comparisons will be adopted through this section.
%
Results are shown at $Q^2 = 10^4 \, \textrm{GeV}^2$ and the residual shift in central values
arising from the profiling is ignored.

%
The effect of including correlated systematic uncertainties is shown in 
Fig.~\ref{fig:profiling_syst}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
The fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2
DIS projections.
%
In the latter case, we consider both only statistical errors and statistical and systematic
errors added in quadrature.
%
The FASER$\nu$2 dataset used here accounts for both  inclusive and charm-tagged structure functions
as well as for outgoing lepton charge-separation.
%
}
\label{fig:profiling_syst}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\paragraph{Dependence with the experiments.}
%
Same as Fig.~\ref{fig:profiling_baseline} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.

\paragraph{Impact of systematic uncertainties.}

\paragraph{Impact of charm production.}
%
Fig.~\ref{fig:profiling_charm} displays a comparison of the baseline LHC neutrino dataset with the results
of profiling without the charm production structure functions. 
Particularly, the constraints on the $s$ PDF are observed to become more stringent 
by virtue of the contribution of the charm production structure functions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{Comparing the results shown in Fig.~\ref{fig:profiling_baseline} (red and blue), 
to the results obtained without charm production structure functions (green).
}
\label{fig:profiling_charm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The role of lepton charge separation.}
%
Fig.~\ref{fig:profiling_nochargediscrimination} compares the baseline LHC neutrino dataset with the results
of a profiling without allowing for the possibility of outgoing lepton charge separation.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{Comparing the results shown in Fig.~\ref{fig:profiling_baseline} (red and blue), 
to the results obtained without identifying the charge of the outgoing lepton (green).
}
\label{fig:profiling_nochargediscrimination}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

For the baseline results, we consider FASER$\nu$2 operative for the full duration
of the HL-LHC data-taking period.
%
Both inclusive and charm-tagged structure functions enter the profiling,
and outgoing lepton charge-separation is assumed.
%
Fig.~\ref{fig:profiling_syst} displays the
fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2 projections.
%
For the latter, we consider two scenarios: first where the covariance matrix includes
only statistical errors, and second with experimental systematic
errors added in quadrature to the statistical ones.
%
Note that the residual shift in central values, which depends on the arbitrary fluctuations
entering the pseudo-data generation, is not displayed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/syst_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
The fractional uncertainties   (68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in PDF4LHC21 compared to the results of its profiling with the FASER$\nu$2
DIS projections.
%
In the latter case, we consider both only statistical errors and statistical and systematic
errors added in quadrature.
%
The FASER$\nu$2 dataset used here accounts for both  inclusive and charm-tagged structure functions
as well as for outgoing lepton charge-separation.
%
}
\label{fig:profiling_syst}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%
Fig.~\ref{fig:profiling_charm} displays a comparison of the baseline LHC neutrino dataset with the results
of profiling without the charm production structure functions. 
Particularly, the constraints on the $s$ PDF are observed to become more stringent 
by virtue of the contribution of the charm production structure functions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive-only_vs_inclusive+charm/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of FASER$\nu$2 structure functions
once charm-tagged measurements are removed.
%
In both cases, the covariance matrix accounts for systematic uncertainties.
}
\label{fig:profiling_charm}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{The role of lepton charge separation.}
%
Fig.~\ref{fig:profiling_nochargediscrimination} compares the baseline LHC neutrino dataset with the results
of a profiling without allowing for the possibility of outgoing lepton charge separation.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/nochargediscrimination/statOnly_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
Same as Fig.~\ref{fig:profiling_syst}, now assessing the impact of that being unable to identify
the charge of the outgoing lepton would have on the FASER$\nu$2 reach on the proton PDFs.
%
In both cases, the covariance matrix accounts for systematic uncertainties.
}
\label{fig:profiling_nochargediscrimination}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf add discussion of experiment sensitivity}

%
Same as Fig.~\ref{fig:profiling_baseline} comparing FASER$\nu$2 with AdvSND and with FASER$\nu$.
